---
title: "Median Price Auction"
author: "Mojtaba Tefagh"
date: "4/9/2019"
output:
  md_document:
    variant: markdown_github
---

We first download the data from the Ethereum blockchain.

```{python}
import pandas as pd
import numpy as np
from web3 import Web3, HTTPProvider


web3 = Web3(HTTPProvider('http://localhost:8545'))

    
class CleanTx():
    """transaction object / methods for pandas"""
    def __init__(self, tx_obj):
        self.hash = tx_obj.hash
        self.block_mined = tx_obj.blockNumber
        self.gas_price = tx_obj['gasPrice']
        self.round_gp_10gwei()
        
    def to_dataframe(self):
        data = {self.hash: {'block_mined':self.block_mined, 'gas_price':self.gas_price, 'round_gp_10gwei':self.gp_10gwei}}
        return pd.DataFrame.from_dict(data, orient='index')

    def round_gp_10gwei(self):
        """Rounds the gas price to gwei"""
        gp = self.gas_price/1e8
        if gp >= 1 and gp < 10:
            gp = np.floor(gp)
        elif gp >= 10:
            gp = gp/10
            gp = np.floor(gp)
            gp = gp*10
        else:
            gp = 0
        self.gp_10gwei = gp


block_df = pd.DataFrame()
for block in range(5000000, 5000100, 1):
    block_obj = web3.eth.getBlock(block, True)
    for transaction in block_obj.transactions:
        clean_tx = CleanTx(transaction)
        block_df = block_df.append(clean_tx.to_dataframe(), ignore_index = False)
block_df.to_csv('tx.csv', sep='\t', index=False)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, warning=FALSE, message=FALSE)

library(tidyverse)
```

```{r}
tx.raw <- as.tbl(read.csv("tx.csv", sep = "\t"))
```

Before we begin, some plots from the raw data (gas price will be normalized later):

```{r}
ggplot(tx.raw,aes(x=block_mined, y=round_gp_10gwei))+geom_point()+labs(title="Gas Price")
ggplot(tx.raw,aes(x=block_mined, y=gas_price))+geom_point()
```

Now, we throw out the `round_gp_10gpwei` column and divide the `gas_price` by $10^8$. Then we group our gas prices data by the blocks and we compute a summary (`min,median,mean,max`). The blocks are consecutive and their numbers are made to start from zero in order to have a bit more visually appealing plots!


```{r}
tx.summary <- tx.raw %>% select(-round_gp_10gwei) %>%
  mutate(gas_price=gas_price/10^8,block_mined=block_mined-min(block_mined)) %>% 
  group_by(block_mined) %>%
  summarise_at(.vars=vars(gas_price),.funs=funs(min(.),median(.),mean(.),max(.)))
```


Here are some plots. `geom_smooth()` uses by default the Local Regression (`loess` for short):

*Loess Regression is the most common method used to smoothen a volatile time series. It is a non-parametric methods where least squares regression is performed in localized subsets, which makes it a suitable candidate for smoothing any numerical vector.*

To show the effectiveness/stability of median over other methods, we plot the data points along with the prediction curve of each (`min,median,mean,max`). Notice the scale of `max` is quite different therefore, although it seems stable its prediction curve has much higher errors than median. See the last two plots to compare the scale of their fluctutations.


```{r}
ggplot(tx.summary,aes(x=block_mined,y=min))+geom_smooth()+geom_point()+labs(title="min of gas prices")
```


```{r}
ggplot(tx.summary,aes(x=block_mined,y=mean))+geom_smooth()+geom_point()+labs(title="mean of gas prices")
```



```{r}
ggplot(tx.summary,aes(x=block_mined,y=max))+geom_smooth()+geom_point()+labs(title="max of gas prices")
```


```{r}
ggplot(tx.summary,aes(x=block_mined,y=median))+geom_smooth()+geom_point()+labs(title="median of gas prices")
```





Here is the max, median, and min statistics summary plot:

```{r}
ggplot(data = tx.raw %>% group_by(block_mined)) + 
       stat_summary(
             mapping = aes(x = block_mined, y = gas_price),
             fun.ymin = min,
             fun.ymax = max,
             fun.y = median
         )+labs(title="Summary of gas_prices")
```


Here is how the mean and median and minimum curves compare:

```{r}
ggplot(tx.summary,aes(x=block_mined))+geom_smooth(aes(y=min,colour="min"))+
  geom_smooth(aes(y=median,colour="median"))+geom_smooth(aes(y=mean,colour="mean"))+labs(title="min_median_mean")+ylab("min_median_mean")+scale_colour_manual(name="legend", values=c("blue", "red","green"))

```

Here is how all curves compare:

```{r}
ggplot(tx.summary,aes(x=block_mined))+geom_smooth(aes(y=mean,colour="mean"))+geom_smooth(aes(y=median,colour="median"))+geom_smooth(aes(y=min,colour="min"))+geom_smooth(aes(y=max,colour="max"))+
  labs(title="Summary gas prices")+ylab("min_median_mean_max")+scale_colour_manual(name="legend", values=c("blue", "red","green","black"))
```

<!-- Let us see how the method `gam` errors compare in each case: -->
<!-- Here you will first need to normalized each column to make this meaningful -->
<!-- ```{r} -->
<!-- gam.med <- gam(min_gas_price~block_mined,data=tx.summary) -->
<!-- gam.med$deviance -->
<!-- ``` -->




